A double-sampling extension of the German National Forest Inventory for design-based small area estimation on forest district levels

### 2018-08-06 Reviews/answer_reviewers.tex

\documentclass{article}
\usepackage{authblk}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[ngerman]{babel}
\usepackage[normalem]{ulem}

%============================================ Define Titlepage & packages =============================================%

\title{Review - revision}

\author{A double-sampling extension of the German National Forest Inventory for design-based small area estimation on forest district levels\\
Andreas Hill, Daniel Mandallaz, Joachim Langshausen}

\usepackage{fancyhdr}     
\usepackage{amsmath} %Paket für erweiterte math. Formeln
\usepackage[labelfont=bf]{caption}
\usepackage[font=footnotesize]{caption}
\usepackage[font=footnotesize]{subcaption}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[final]{pdfpages}
\usepackage{color}

\usepackage{geometry}
\geometry{
	a4paper,
	left=25mm,
	right=25mm,
	top=30mm,
	bottom=30mm
}

\setlength{\parindent}{0em} % Einzug bei neuen Absätzen

%------------------------------------------------------------------------------------------------%
% -------------------------------------- Main Document------------------------------------------ %

\begin{document}

%------------------------------------------------------------------------------------------------%
% -------------------------------------- Tex Settings ------------------------------------------ %

\maketitle
\thispagestyle{empty}
\newpage

\pagenumbering{arabic}
\setcounter{page}{1}

\pagestyle{fancy} %Kopfzeile und Fusszeile
\fancyfoot[C]{\thepage}
\setlength{\headsep}{15mm}

\definecolor{mybrown}{rgb}{0.6, 0.15, 0.1}
\definecolor{amaranth}{rgb}{0.9, 0.17, 0.31}
\definecolor{mygreen}{rgb}{0.1, 0.4, 0.4}
\newcommand{\answer}[1]{\small \color{mybrown}{#1} \color{black}}
\newcommand{\note}[1]{\textit{\small \color{amaranth} \textbf{Note:} #1} \color{black}}
\newcommand{\todo}[1]{\color{red}{#1} \color{black}}
\newcommand{\answerfin}[1]{\small \color{mygreen}{#1} \color{black}}

%------------------------------------------------------------------------------------------------%
% ---------------------------------- Reviewer 1 ------------------------------------------------ %

\section*{Reviewer 1:}

I have only a single marginal question, and probably I am wrong: $Z_{c}(x)$ is introduced as a row vector in line 183 and Eqs. 9a and 9b, but it is used as column vector in Eqs. 12, 13 and 14. I would appreciate much if the authors could check whether this inconsistency really exists with respect to notation of $Z_{c}(x)$.\\

Answer:\\

\answerfin{Vectors are always column vectors, i.e $Z(x)$ and $Z_{c}(x)$ are column vectors.	When they are used for predictions they have to be transposed in order to get a scalar product written as a matrix multiplication, i.e. $\pmb{Z}_{c}^{\top}(x)\hat{\pmb{\beta}}_{c,s_2}$. We added the information that $Z_{c}(x)$ is a column vector in line 183 to make this more clear for the reader.}

%------------------------------------------------------------------------------------------------%
% ---------------------------------- Reviewer 2 ------------------------------------------------ %

\section*{Reviewer 2:}

General comment on publishing the article in Remote Sensing:

We decided to hand in our article to be published in the \textit{Remote Sensing} special issue \textit{Remote sensing based Forest Inventories from Landscape to Global Scale}, since multiple of the mentioned topics for articles of the special issue are covered by our article (such as 'Application of remote-sensing techniques for monitoring forest attributes at the forest enterprise level', 'Application of remote-sensing techniques for monitoring forest attributes for national forest inventories', 'Large scale in-situ data requirement and sampling design for monitoring forest ecosystems with remote-sensing techniques').  Additionally, of course, not all readers of \textit{Remote Sensing} are specialists in forest inventory, but most of the latter frequently read \textit{Remote Sensing}.

\begin{enumerate}

  % 01) ++++++++++++++++++++++++++ %
  \item \textit{L28: “entire forest state area of Germany” I understand what you mean, but it may be misleading as readers might think about the area owned by the German state forest enterprise (Bundesforst). I would suggest to rephrase “forested area of Germany”.}

  \answerfin{Has been changed accordingly.}
  % --------------------------- %

  % 02) ++++++++++++++++++++++++++ %
  \item \textit{L29: 114'191 ha – A wrong unit was used here, its 114 191 km$^2$ (or 11 419 124 ha)..}

  \answerfin{Has been corrected accordingly.}  
  % --------------------------- %

   % 03) ++++++++++++++++++++++++++ %
  \item \textit{L36: “standwise forest inventories (SFI)”?}

  \answerfin{Has been changed accordingly.}  
  % --------------------------- %

  % 04) ++++++++++++++++++++++++++ %
  \item \textit{L38-41: Please add the information that the FDI of Lower-Saxony (Betriebsinventur, BI) is only done for forests owned by the state forest enterprise (Lower Saxony State Forests = Niedersächsische Landesforsten, NLF)}

  \answerfin{The information has been added.}  
  % --------------------------- %

  % 05) ++++++++++++++++++++++++++ %
  \item \textit{L41 As far as I remember, [4] is an article written in German. If so, please indicate in the reference list – it is annoying for readers to search for papers that turn out to be written in a language they possibly do not understand.}

  \answerfin{We now give the original title in German.}  
  % --------------------------- %

  % 06) ++++++++++++++++++++++++++ %
  \item \textit{L42: As far as I remember, v.Lüpke’s dissertation [5] is a cumulative work. If so, please cite the original articles and not the compilation.}

  \answerfin{Has been changed accordingly.}  
  % --------------------------- %

  % 07) ++++++++++++++++++++++++++ %
  \item \textit{L43: I would suggest to cite the classic textbooks of Cochran (1977) and de Vries (1986) beside the modern literature [6-9] }

  \answerfin{The respective citations have been added.}  
  % --------------------------- %

  % 08) ++++++++++++++++++++++++++ %
  \item \textit{L43-48: I would suggest to add some words (here or in the discussion) addressing the problems arising with multi-purpose forest inventories (e.g. Corona and Marchetti 2007): The stratification is optimized for a single target variable (in most cases the volume of the growing stock) and the introduction of additional target variables becomes challenging (e.g. Ritter and Saborowski, 2014).}

  \answerfin{We think that the reviewer might mix up \textit{stratification} (where the sample sizes are optimized for strata \textit{prior} to the actual conduction of the inventory based on auxiliary data) with \textit{post-stratification} (where the categorical auxiliary data are used in the regression model \textit{after} the inventory has been conducted). The latter, which is the case applied in our article, does not impose any of the mentioned problems of multi-objective optimization. We thus think that including this topic does not fit well into our article since it is not affecting the methods that we are demonstrating.}

%  \note{I don't think this issue concerns the work presented in our study, since optimization was not part of the study. One could mention the anticipated variance treated in the book of Mandallaz (2008). Multi-objective optimization would implies a weighting of the objectives, which is a highly political issue and probably unsolvable in my opinion. Separate investigation are probably simpler and better. Worth emphasizing that the method presented is valid for any response variable which can be used to define a local density. I also think that the reviewer exchanges stratification (where the sample sizes are optimized prior to the actual conduction of the inventory based on auxiliary data) and post-stratification (where the categorical auxiliary data are used in the regression model after the inventory has been conducted). The latter, which is the case applied in our article, does not impose any of the mentioned problems of multi-objective optimization. We thus think that including this topic does not fit well into our article since it is not affecting the methods we suggest.}
  % --------------------------- %

  % 09) ++++++++++++++++++++++++++ %
  \item \textit{L46-47: Double-sample procedures have not only been used in the FDI of Lower Saxony, but also in the NFIs of Canada (Gillis et al., 2010) and Switzerland (Lanz et al. 2010), and in different other inventories (e.g. Chojnacky, 1998 or  Gasparini et al., 2010).}

  \answerfin{We rephrased the sentence and added the suggested references.}  
  % --------------------------- %

  % 10) ++++++++++++++++++++++++++ %
  \item \textit{L99 “The German NFI (Bundeswaldinventur, BWI)“  I think, the abbreviation introduced in the next line becomes more meaningful when giving the German name here.}

  \answerfin{Has been changed.}  
  % --------------------------- %

  % 11) ++++++++++++++++++++++++++ %
  \item \textit{L100 “The third and most recent” }

  \answerfin{Has been changed.}  
  % --------------------------- %

  % 12) ++++++++++++++++++++++++++ %
  \item \textit{L101 '4x4km' I would prefer '4km ' 4km'}

  \answerfin{We would like to stick to the given notation in accordance with our previously published article (Hill et. al 2018: Combining canopy height and tree species map information for large-scale timber volume estimations under strong heterogeneity of auxiliary data and variable sample plot sizes, \textit{European Journal of Forest Research}).}  
  % --------------------------- %

  % 13) ++++++++++++++++++++++++++ %
  \item \textit{L102 '2x2km' same as above (2km ' 2km)}

  \answerfin{Same as above.}  
  % --------------------------- %

  % 14) ++++++++++++++++++++++++++ %
  \item \textit{L107: A short explanation of the angle count sampling concept would be helpful for readers who aren't foresters, maybe here or in a corresponding appendix.}

  \answerfin{We added an explanation of angle count sampling in Section 2.}  
  % --------------------------- %

  % 15) ++++++++++++++++++++++++++ %
  \item \textit{L110/111 “DBH” and “DBH” Please decide whether or not to use italics. Please also add the information that this refers to a height of 1.3 m, Remote Sensing has a lot of readers who are not foresters.}

  \answerfin{We added the information about the height. Concerning italics, we decided to use italics when first introducing a notation/term and use normal formatting when using the term afterwards.}  
  % --------------------------- %

  % 17) ++++++++++++++++++++++++++ %
  \item \textit{L196 Please also provide reference to the R software itself, and not only to the package. }

  \answerfin{The reference has been added.}  
  % --------------------------- %

  % 18) ++++++++++++++++++++++++++ %
  \item \textit{L273: I think this is the only occasion you use italics for "RLP".}

  \answerfin{We use italics when introducing a term for the first time and use normal formatting when using the term afterwards.}  
  % --------------------------- %

  % 19) ++++++++++++++++++++++++++ %
  \item \textit{L283: “communal forests” is most often used as a synonym for “community forests” in context of rural development policy. I think here it is rather an odd translation of the German word “Kommunalwald”. Maybe, “municipal forests” is the better translation.}

  \answerfin{We changed 'communal' to 'municipal' throughout the entire article.}  
  % --------------------------- %

  % 20) ++++++++++++++++++++++++++ %
  \item \textit{L295 "RLP" was already introduced as an abbreviation}

  \answerfin{'RLP' has been deleted.}  
  % --------------------------- %

  % 21) ++++++++++++++++++++++++++ %
  \item \textit{L287: Instead of “45 Forstämter (FA)” I would use “45 forest districts (Forstämter, FA)” }

  \answerfin{Has been changed, and likewise for the Forstreviere which we now call sub-districts.}  
  % --------------------------- %

  % 22) ++++++++++++++++++++++++++ %
  \item \textit{L289-290: If the SFI is conducted in a five year cycle, shouldn’t the management strategy be also set up for five years, instead of ten years?}

  \answerfin{The cycle of the stand wise inventories actually varies between 5 and 10 years and can in some cases even exceed 10 years. The stand wise inventories and the date of their conduction are planned by the state forest service. The management strategy for the stands is, however, always made for the upcoming 10 years ('mittelfristige Planung').}  
  % --------------------------- %

  % 23) ++++++++++++++++++++++++++ %
  \item \textit{L295 "2x2km" (see above)}

  \answerfin{We would like to keep the '2x2km' notation.}  
  % --------------------------- %

  % 24) ++++++++++++++++++++++++++ %
  \item \textit{Figure 1: "communal forests" (see above)}

  \answerfin{Has been corrected.}  
  % --------------------------- %

  % 25) ++++++++++++++++++++++++++ %
  \item \textit{Table 1: Please remove the digits (or at least reduce the number of digits). Giving values with an “accuracy” of 1/100th of a mm (i.e. 10 mm) for DBH, as an example, really does not make much sense. }

  \answerfin{We limited the number of digits for timber volume, DBH and height to one digit and removed the digits for stem number.}  
  % --------------------------- %

  % 26) ++++++++++++++++++++++++++ %
  \item \textit{Table 3: I think one digit for the percentage values should be enough.}

  \answerfin{Has been changed accordingly.}  
  % --------------------------- %

  % 27) ++++++++++++++++++++++++++ %
  \item \textit{Table 6: Please indicate for what variable point estimates are. I suppose it is volume of growing stock per area unit [m$^3$ha-1]? And again, check the number of digits.}

  \answerfin{Yes! We added the missing information accordingly.}  
  % --------------------------- %

 % 28) ++++++++++++++++++++++++++ %
  \item \textit{L454-458 I understand your intention and the necessity of removing FR-units. However, when comparing the performance of the estimators you should use the same population for all estimators. Removing the "difficult" FR-units (i.e. those with a low sampling density) only for PSMALL and EXTPSYNTH is somewhat unfair against the other estimators, and may bias the results. So, my advice is to recalculate SRS and PSYNTH for the same 321 FRs that were used for PSMALL and EXTPSYNTH. Edit: I noticed you confined your analyses to those 321 FRs later on (Fig 5 and Tab. 7), another reason to also do it here.}

  \answerfin{We changed the evaluation according to your suggestion and added a sentence in the paragraph above the table. The descriptive summary statistics for the one-phase SRS and the PSYNTH estimator did only differ marginally, with exception of the maximal errors which logically turned out to be lower. We also adjusted the numbers given in Section 6.2 and the graphic of Figure 3 respectively.}

  % --------------------------- %

 % 29) ++++++++++++++++++++++++++ %
  \item \textit{L517: Please use the same scaling for both x- and y-axis on the left plot. It is irritating that the 1:1 line does not cross the grid-corners.}

  \answerfin{Has been changed accordingly.}  
  % --------------------------- %

   % 30) ++++++++++++++++++++++++++ %
  \item \textit{L655-656: "Northwest German Forest Research Institution" It should be "Institute" instead of "Institution"}

  \answerfin{Has been corrected.}  
  % --------------------------- %

\end{enumerate}

%------------------------------------------------------------------------------------------------%
% ---------------------------------- Reviewer 3 ------------------------------------------------ %

\section*{Reviewer 3:}

\begin{enumerate}

    % 01) ++++++++++++++++++++++++++ %
  	\item \textit{Under the design-based inferential framework, invoking the asymptotical properties of a small-area estimator is a contradiction in terms; the asymptotic properties are based on large-sample assumptions, while SAE estimators are used when the sample size is (too) small. If the sample size for the entire population is very large, then the small-area estimation becomes a common domain estimation problem, and there is no need for tailored SA estimators because the direct estimators are probably the most efficient -  see Estevao and Särndal (2004) 'Borrowing strength is not the best technique within a wide class of design-consistent domain estimators.  Journal of Official Statistics, 20, 645-669' for details. This is an important aspect that it’s been often ignored in the model-assisted SA studies. The authors put a great deal of effort in assessing the results by the realized sample sizes in various SAs, however, such comparisons have limited relevance if the asymptotic results cannot be invoked. This is not criticism, personally I do not have a solution, and there is probably no analytical solution to derive the small-sample properties of these estimators. However, I think that rising this issue would add value to the manuscript, by informing the readers of potential drawbacks of the estimation methods.}

%  	\note{ the populations are domains (i.e. a continuum of infinitely many points) of the plane F, also known as the Monte Carlo approach: the objective is to estimate the integral $\int_{G} Y(x)dx$, $G \in F$ a function $Y(x)$ which is essentially the Horwitz-Thompson estimator for a response variable for the population of trees. This is the main difference with standard survey sampling. Another important difference is that instead of having a single large sample we have $n_2$ points $x$	each one with a sample of trees (terrestrial sample). The sample size $n_2$ can be large over the entire domain, but small over sub-domains, and too small to fit models using auxiliary data available at a much larger number of points $n_1$. You do not have to borrow strength if you are strong, which is obvious. We do not propose to fit models over extremely large areas with very different forest structures (say all Europe) but to rely on predictions based on remote sensing data to provide better estimates for smaller management units. Asymptotic results for the variances are, given the complexity of the problem, the only available ones. When are asymptotic results approximately valid? Take for instance n=6 (not a very large number), then the distribution of the mean of n=6 uniformly distributed random variables is practically undistinguishable from the normal distribution, so that in this case n=6 is the asymptotic validity range. On the other hand with extreme values statistics, n=100 can be far to small to reach a normal distribution. Some simulations performed on the artificial examples (see our articles published in the Canadian Journal of Forest Research - Source) and on a unique data set (Zurichberg data, see book of Mandallaz for examples) show that for SA problems, $n$ > 12 or even 6 is acceptable. All the variance estimates are based on the asumption of i.i.d uniformly distributed points (or clusters origins) for remote sensing for remote sensing followed by SRS selection for terrestrial observations, whereas in practice systematic grids are used. Simulation and past experience with alternative model-dependent Kriging procedure (Source) show that the variance estimates are usually to pessimistic. On the other hand, only sampling errors are taken into account and not measurement errors (e.g. on bole volume).}

  	\answerfin{Asymptotic results for the variances are, given the complexity of the problem, the only available ones. When are asymptotic results approximately valid? If one takes for instance n=6 (not a very large number), then the distribution of the mean of n=6 uniformly distributed random variables is practically undistinguishable from the normal distribution, so that in this case n=6 is the asymptotic validity range. On the other hand with extreme values statistics, n=100 can be far to small to reach e.g. the Gumbel distribution. Transferring this to the case of forest inventory, it is actually impossible to define a minimal sample size that always ensures the validity of the central limit theorem for the particular case. However, simulations performed for an artificial example in Mandallaz et al. (2013). New regression estimators in forest inventories with two-phase sampling and partially exhaustive information: a design-based monte carlo approach with applications to small-area estimation. \textit{Canadian Journal of Forest Research}, 43(11), 1023-1031, suggested that for SA problems, a sample size in a small area of $n$ > 6 is acceptable to reach the nominal coverage rates of the confidence intervals. Whereas these simulations where performed for simple sampling, re-evaluating the simulation example recently confirmed the same results for cluster sampling. We added a respective remark in the discussion, Section 7.1, line 638-645.}

### 2018-08-06 Reviews/hill et al 2018.tex
update 06_08_2018
final version of published article

The German National Forest Inventory (NFI) provides reliable evidence-based and accurate information of the current state and the development of Germany's forest over time. The NFI thereby has the responsibility to satisfy various information needs including reporting to public and state forestry administrations, wood-based industries and the public on the national level, as well as to the Food and Agriculture Organization of the United Nations (FAO) and to the United Nations Framework Convention on Climate Change (UNFCC) on the international level \citep{polley2010intomppo}. The current design of the German NFI rests solely upon a terrestrial cluster inventory that is carried out at sample locations systematically distributed over the entire forest state area of Germany. In order to cover a large area of 114'191 ha \citep{bwi3}, the sample size has been specifically chosen to satisfy high estimation accuracies for forest attributes on the national and federal state levels. However, sample sizes often drop dramatically when entering spatial units below the federal state level. This is particularly true for forest management levels such as forest districts for which the estimation uncertainties turn out to be unacceptably large due to the very limited number of sample plots within these units. For this reason, the German NFI data have not yet been extensively incorporated into operational planning on forest district management levels. In most German federal states, management strategies are thus still based on expert judgments from time-consuming standwise inventories (SFI), which are prone to systematic deviations \cite{kulievsis2016} and do not provide any measure of uncertainty.\par

Some German federal states, such as Lower Saxony, have approached this problem by establishing a regional Forest District Inventory (FDI) with a much higher sampling density than used by the NFI in order to scientifically base their regional management strategies on quantitative and accurate information \citep{bockmann1998}. However, such FDIs are cost-intensive and, facing increasing restrictions in budget and staff resources, there has been a need for more cost-efficient inventory methods \citep{vonluepke2013}. One method which has proven to be efficient is double- or two-phase sampling \citep{sarndal2003, gregoire2007, kohl2006, mandallaz2008}. Double-sampling incorporates less expensive auxiliary information and can be used to either increase estimation precision under a fixed terrestrial sample size, or maintain estimation precision under reduced terrestrial sample size. Double-sampling procedures have already been used for stratification in the FDI of Lower Saxony \citep{saborowski2010}, and \citet{grafstrom2017a} illustrated how to use the auxiliary information to determine optimised balanced terrestrial sample designs. Recent studies have extended double-sampling to triple-sampling estimation methods using auxiliary information derived at two different sampling intensities. An example can be found in \citet{vonLuepke2012} who illustrated an extension of the existing two-phase FDI of Lower Saxony to a three-phase design that uses updates of past inventory data as additional auxiliary information and allows for a significant reduction of the terrestrial sample size in intermediate inventories. Another example is \citet{massey2014a} who developed a triple-sampling extension based on the ideas of \citet{mandallaz2013c} for the Swiss NFI that can significantly reduce the increase in estimation uncertainty caused by the new annual inventory design.\par

@@

The German NFI is a periodic inventory that is carried out every 10 years over the entire forest area of Germany. The most recent inventory (BWI3) was conducted in 2011 and 2012. While information was originally gathered on a systematic 4x4 km grid, some federal states such as Rhineland-Palatinate have switched to a densified 2x2 km grid. The German NFI uses a cluster sampling design, which means that a sample unit consists of at most four sample locations (also referred to as \textit{sample plots}) that are arranged in a square, called \textit{cluster}, with a side length of 150 metres. The number of plots per cluster can vary between 1 and 4 depending on forest/non-forest decisions by the field crews on the individual plot level \citep{bwi3_aufn}. In the field survey of the BWI3, sample trees for timber volume estimation are selected according to the angle count sampling technique \citep{bitterlich1984}, using a basal area factor ($BAF$) of 4 that is respectively adjusted for sample trees at the forest boundary by a geometric intersection of the boundary transect with the individual tree's inclusion circle \citep{bwi3_aufn}. A further inventory threshold for a tree to be recorded is a diameter at breast height ($DBH$) of at least 7 cm. For each sample tree that is selected by this procedure, the DBH, the absolute tree height, the tree diameter at 7 m ($D7$) and the tree species is measured and used to estimate the volume at the tree level. These volume estimates are based on the application of tree species specific taper curves that are adjusted to the set of diameters and corresponding height measurements taken from the respective sample tree \citep{kublin2013}.

@@

\noindent $\pmb{Z}_{c}(x)$ is the vector of explanatory variables on the cluster level, which is calculated as the weighted average of the explanatory variables $\pmb{Z}(x_l)$ on the individual plot levels $x_1, ..., x_l$ (Eq.\ref{eq:Zc(x)}). The weight $w(x_l)$ is the proportion of the extraction area (support) within the forest $F$ used to derive the explanatory variables from the raw auxiliary information.

@@

\noindent being the empirical model residuals at the cluster level, which by construction of OLS satisfy the important zero mean residual property, i.e. $\frac{\sum_{x \in s_{2}} M(x) \hat{R}_{c}(x)}{\sum_{x \in s_{2}} M(x)}=0$.\\

In the following, we will give a short description of each small area estimator and refer to \citet{mandallaz2013a, mandallaz2016, mandallaz2013b} if the reader requires additional details or proofs. The estimators have also been implemented in the R-package \textit{forestinventory} \citep{forestinventory} which was used to compute all estimates in this study.\\

@@

The \psynth{} estimator is commonly applied when no terrestrial sample is available within the small area $G$ (i.e. $n_{2,G}=0$). The point estimate (Eq. \ref{eq:psynth_pest}) is thus only based on the predictions generated by applying the globally derived regression coefficients to the small area cluster means of the explanatory variables $\hat{\bar{\pmb{Z}}}_{c,G}$. Note that the bias correction term using the empirical residuals (Eq. \ref{eq:psmall_pest}) can no longer be applied. The \psynth{} estimator thus has a potential unobservable design-based bias.

@@

The contribution to the variance by the model residuals in small area $G$ can also no longer be considered (Eq. \ref{eq:psynth_var}). As a result, the synthetic estimator will usually have a smaller variance than estimators that consider the model residuals, but at the cost of a potential bias. Note that the \psynth{} estimator is still design-based, but one purely has to rely on the validity of the regression model within the small area as it is the case in the model-dependent framework.\\

@@

The German federal state Rhineland-Palatinate (\textit{RLP}) is located in the western part of Germany and borders Luxembourg, France and Belgium. With 42.3\% (appr. 8400 km$^2$) of the entire state area (19850 km$^2$) covered by forest, RLP is one of the two states with the highest forest coverage among all federal states of Germany \citep{bwi3}. The forests of RLP are further characterised by a pronounced diversity in bioclimatic growing conditions that have strong influence on the local growth dynamics as well as tree species composition \citep{gauer2005} and are further characterised by large variety of forest structures ranging from characteristic oak coppices (Moselle valley), pure spruce, beech and scots pine forests (i.a. Hunsr{\"u}ck and Palatinate forest) up to mixed forests comprising variable proportions of oak, larch, spruce, Scots pine and beech. Around 82\% of the forest area in RLP are mixed forest stands and 69\% of the forest area exhibit a multi-layered vertical structure. The forest area of RLP are divided into 3 ownership classes, i.e. state forest (27\%), communal forest (46\%) and privately owned forest (27\%). The forest service of RLP has the legal mandate to sustainably manage the state and communal forest area (73\% of the entire forest area), including forest planning, harvesting and the sale of wood \citep{lwaldg_rlp}. For this reason, the entire forest area has been spatially organised in 3 main hierarchical management units (Figure \ref{fig:StudyArean}). On the upper level, RLP has been divided into 45 Forst{\"a}mter (\textit{FA}), which are further divided into a total number of 405 Forstreviere (\textit{FR}). The next level are the forest stands (104'184 in total) for which expert judgements are conducted by SFIs in a 5 to 10 year period in order to set up management strategies for the upcoming 10 years. The FAs and FRs constituted the SA units for which design-based small area estimations of the mean standing timber volume were calculated by incorporating the available terrestrial inventory data of the BWI3 in the estimators described in Section \ref{sec:estimators}. The average area of the SA units was 43'777 ha on the FA-level, and 4624 ha on the FR level.

>>>>

The German National Forest Inventory (NFI) provides reliable evidence-based and accurate information of the current state and the development of Germany's forest over time. The NFI thereby has the responsibility to satisfy various information needs including reporting to public and state forestry administrations, wood-based industries and the public on the national level, as well as to the Food and Agriculture Organization of the United Nations (FAO) and to the United Nations Framework Convention on Climate Change (UNFCC) on the international level \citep{polley2010intomppo}. The current design of the German NFI rests solely upon a terrestrial cluster inventory that is carried out at sample locations systematically distributed over the entire forested area of Germany. In order to cover a large area of 114'191 km$^2$ \citep{bwi3}, the sample size has been specifically chosen to satisfy high estimation accuracies for forest attributes on the national and federal state levels. However, sample sizes often drop dramatically when entering spatial units below the federal state level. This is particularly true for forest management levels such as forest districts for which the estimation uncertainties turn out to be unacceptably large due to the very limited number of sample plots within these units. For this reason, the German NFI data have not yet been extensively incorporated into operational planning on forest district management levels. In most German federal states, management strategies are thus still based on expert judgements from time-consuming standwise forest inventories (SFI), which are prone to systematic deviations \cite{kulievsis2016} and do not provide any measure of uncertainty.\par

Some German federal states, such as Lower Saxony, have approached this problem by establishing a regional Forest District Inventory (FDI) carried out for forests owned by the state forest enterprise with a much higher sampling density than used by the NFI in order to scientifically base their regional management strategies on quantitative and accurate information \citep{bockmann1998}. However, such FDIs are cost-intensive and, facing increasing restrictions in budget and staff resources, there has been a need for more cost-efficient inventory methods \citep{vonLuepke2012, vonluepke2013}. One method which has proven to be efficient is double- or two-phase sampling \citep{devries1986, cochran1977, sarndal2003, gregoire2007, kohl2006, mandallaz2008}. Double-sampling incorporates less expensive auxiliary information and can be used to either increase estimation precision under a fixed terrestrial sample size, or maintain estimation precision under reduced terrestrial sample size.

Double-sampling procedures have already been used in various countries such as Canada \citep{gillis2010intomppo}, the USA \citep{chojnacky1998}, Switzerland \citep{lanz2010intomppo}, Italy \citep{gasparini2010intomppo} and Germany \citep{saborowski2010}. Recent studies from \citet{grafstrom2017a} illustrated how to use the auxiliary information to determine optimised balanced terrestrial sample designs. Double-sampling has also been extended to triple-sampling estimation methods using auxiliary information derived at two different sampling intensities. An example can be found in \citet{vonLuepke2012} who illustrated an extension of the existing two-phase FDI of Lower Saxony to a three-phase design that uses updates of past inventory data as additional auxiliary information and allows for a significant reduction of the terrestrial sample size in intermediate inventories. Another example is \citet{massey2014a} who developed a triple-sampling extension based on the ideas of \citet{mandallaz2013c} for the Swiss NFI that can significantly reduce the increase in estimation uncertainty caused by the new annual inventory design.\par

@@

The German NFI (Bundeswaldinventur, BWI )is a periodic inventory that is carried out every 10 years over the entire forest area of Germany. The third and most recent inventory (BWI3) was conducted in 2011 and 2012. While information was originally gathered on a systematic 4x4 km grid, some federal states such as Rhineland-Palatinate have switched to a densified 2x2 km grid. The German NFI uses a cluster sampling design, which means that a sample unit consists of at most four sample locations (also referred to as \textit{sample plots}) that are arranged in a square, called \textit{cluster}, with a side length of 150 metres. The number of plots per cluster can vary between 1 and 4 depending on forest/non-forest decisions by the field crews on the individual plot level \citep{bwi3_aufn}. In the field survey of the BWI3, sample trees for timber volume estimation are selected according to the angle count sampling technique \citep{bitterlich1984}. Angle count sampling is a visual selection procedure conducted via an optical instrument (\textit{Relascope}). At a sample point $x$, a tree is selected as a sample tree if its apparent diameter at the height of 1.3 m ($DBH$) and the associated angle $\alpha_i$ (in radiant) appears larger than a limit angle $\alpha$ when viewed through the Relascope \citep{mandallaz2008}. The limit angle $\alpha{}$ can be expressed by the so-called basal area factor ($BAF$), i.e. $BAF = 10^{2}sin^{2}(\frac{\alpha}{2})$. Consequently, each tree $i$ is assigned with an individual radius $R_{i}=\frac{DBH_{i}}{2\sqrt{BAF}}$ which is the distance between the tree location and the sample plot center. A tree is selected if $R_{i}$ is equal to or smaller than the so-called limiting distance $R$ that results from chosen BAF (i.e., $\alpha$). One characteristic of angle count sampling is that a sample plot does no longer has a fixed radius in which sample trees are selected, but each tree creates its individual radius $R_i$ that is - likewise the associated inclusion probability - proportional to its basal area. For this reason, the angle count method is also referred to as \textit{variable radius plot sampling} and implements the \textit{probability proportional to size (PPS)} concept. The BWI3 uses a basal area factor of 4 that is respectively adjusted for sample trees at the forest boundary by a geometric intersection of the boundary transect with the individual tree's inclusion circle \citep{bwi3_aufn}. A further inventory threshold for a tree to be recorded is a DBH of at least 7 cm. For each sample tree that is selected by this procedure, the DBH, the absolute tree height, the tree diameter at 7 m ($D7$) and the tree species is measured and used to estimate the volume at the tree level. These volume estimates are based on the application of tree species specific taper curves that are adjusted to the set of diameters and corresponding height measurements taken from the respective sample tree \citep{kublin2013}.

@@

\noindent $\pmb{Z}_{c}(x)$ is the column vector of explanatory variables on the cluster level, which is calculated as the weighted average of the explanatory variables $\pmb{Z}(x_l)$ on the individual plot levels $x_1, ..., x_l$ (Eq.\ref{eq:Zc(x)}). The weight $w(x_l)$ is the proportion of the extraction area (support) within the forest $F$ used to derive the explanatory variables from the raw auxiliary information.

@@

\noindent being the empirical model residuals at the cluster level. By construction of OLS, the empirical model residuals satisfy that they average to zero, i.e. $\frac{\sum_{x \in s_{2}} M(x) \hat{R}_{c}(x)}{\sum_{x \in s_{2}} M(x)}=0$, if $\pmb{Z}_{c}(x)$ contains the intercept term 1. Because the model is fitted internally, i.e. using the terrestrial sample $s_2$ of the inventory area, this leads to the important \textit{zero mean residual property} of the theoretical model residuals over the inventory domain $F$, i.e. $\int_{F} R_{c}(x)dx$. \citet{mandallaz2013a} and \citet{mandallaz2013b} used this property particular for the case of small area estimation to derive better variance estimates based on the g-weight technique adapted from the works of \citet{sarndal2003}.\\

In the following, we will give a short description of each small area estimator and refer to \citet{mandallaz2013a, mandallaz2016, mandallaz2013b} if the reader requires additional mathematical details or proofs. The estimators have also been implemented in the open-source software-package \textit{forestinventory} \citep{forestinventory} in the statistical software \textit{R} \citep{R} which was used to compute all estimates in this study.\\

@@

The \psynth{} estimator is commonly applied when no terrestrial sample is available within the small area $G$ (i.e. $n_{2,G}=0$). The point estimate (Eq. \ref{eq:psynth_pest}) is thus only based on the predictions generated by applying the globally derived regression coefficients to the small area cluster means of the explanatory variables $\hat{\bar{\pmb{Z}}}_{c,G}$. Note that the bias correction term using the empirical residuals (Eq. \ref{eq:psmall_pest}) can no longer be applied. Conditioned on the realized sample, the \psynth{} estimator can thus potentially have an unobservable design-based bias.

@@

The contribution to the variance by the model residuals in small area $G$ can also no longer be considered (Eq. \ref{eq:psynth_var}). As a result, the synthetic estimator will usually have a smaller variance than estimators that consider the model residuals, but at the cost of a potential bias. Note that the \psynth{} estimations are still design-based, but one purely has to rely on the validity of the regression model within the small area as it is the case in the model-dependent framework.\\

@@

The German federal state Rhineland-Palatinate (\textit{RLP}) is located in the western part of Germany and borders Luxembourg, France and Belgium. With 42.3\% (appr. 8400 km$^2$) of the entire state area (19850 km$^2$) covered by forest, RLP is one of the two states with the highest forest coverage among all federal states of Germany \citep{bwi3}. The forests of RLP are further characterised by a pronounced diversity in bioclimatic growing conditions that have strong influence on the local growth dynamics as well as tree species composition \citep{gauer2005} and are further characterised by large variety of forest structures ranging from characteristic oak coppices (Moselle valley), pure spruce, beech and scots pine forests (i.a. Hunsr{\"u}ck and Palatinate forest) up to mixed forests comprising variable proportions of oak, larch, spruce, Scots pine and beech. Around 82\% of the forest area in RLP are mixed forest stands and 69\% of the forest area exhibit a multi-layered vertical structure. The forest area of RLP are divided into 3 ownership classes, i.e. state forest (27\%), municipal forest (46\%) and privately owned forest (27\%). The forest service of RLP has the legal mandate to sustainably manage the state and municipal forest area (73\% of the entire forest area), including forest planning, harvesting and the sale of wood \citep{lwaldg_rlp}. For this reason, the entire forest area has been spatially organised in 3 main hierarchical management units (Figure \ref{fig:StudyArean}). On the upper level, RLP has been divided into 45 forest districts (Forst{\"a}mter, \textit{FA}), which are further divided into a total number of 405 sub-districts (Forstreviere, \textit{FR}). The next level are the forest stands (104'184 in total) for which expert judgements are conducted by SFIs in a 5 to 10 year period in order to set up management strategies for the upcoming 10 years. The FAs and FRs constituted the SA units for which design-based small area estimations of the mean standing timber volume were calculated by incorporating the available terrestrial inventory data of the BWI3 in the estimators described in Section \ref{sec:estimators}. The average area of the SA units was 43'777 ha on the FA-level, and 4624 ha on the FR level.
